---
title: "Comparison fits of the multiplicative structural mean model"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Comparison fits of the multiplicative structural mean model}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(OneSampleMR)
if (requireNamespace("ivtools", quietly = TRUE)) library(ivtools)
```

## Comparison fit using the ivtools package

* Example from the `ivtools::ivglm()` helpfile. First simulate some example data.

```{r}
set.seed(12345)
n <- 5000
psi0 <- 0.5
psi1 <- 0.2
Z <- rbinom(n, 1, 0.5)
X <- rbinom(n, 1, 0.7*Z + 0.2*(1 - Z)) 
m0 <- plogis(1 + 0.8*X - 0.39*Z)
Y <- rbinom(n, 1, plogis(psi0*X + log(m0/(1 - m0)))) 
dat <- data.frame(Z, X, Y)
```

* Then fit MSMM using G-estimation.

```{r}
if (requireNamespace("ivtools", quietly = TRUE)) {
  fitZ.L <- glm(Z ~ 1, family = "binomial", data = dat)
  fitY.LZX <- glm(Y ~ X, family = "binomial", data = dat)
  fit01 <- ivglm(estmethod = "g", X = "X", Y = "Y",
                    fitZ.L = fitZ.L, fitY.LZX = fitY.LZX, 
                    data = dat, link = "log")
  print(summary(fit01))
  print(confint(fit01))
} else {
  print("The ivtools package is not available, so this example was not run")  
}
```

* Back transforming that estimate from the $\log(\text{CRR})$ scale to the $\text{CRR}$ scale.

```{r}
if (requireNamespace("ivtools", quietly = TRUE)) {
  print(exp(cbind(fit01$est, confint(fit01))))
} else {
  print("The ivtools package is not available, so this example was not run")  
}
```

* Comparison fit using `msmm()`.

```{r}
fit02 <- msmm(Y ~ X | Z, data = dat)
summary(fit02)
```

* Comparison fit using the alternative GMM moment conditions.

```{r}
fit03 <- msmm(Y ~ X | Z, data = dat, estmethod = "gmmalt")
summary(fit03)
```

* Comparison fit using transformed variables using two-stage least squares.

```{r}
fit04 <- msmm(Y ~ X | Z, data = dat, estmethod = "tsls")
summary(fit04)
```

* Comparison fit using the alternative transformed variables approach using two-stage least squares.

```{r}
fit05 <- msmm(Y ~ X | Z, data = dat, estmethod = "tslsalt")
summary(fit05)
```
